The interactions of rational, pragmatic agents\\ lead to efficient language structure and use

### 2019-02-01 paper/paper.tex
more tweaks

The approaches above typically posit efficiency measures motivated by
information-theoretic principles, but not directly grounded in language
use by interacting agents. In this work, we derive a measure of
efficiency from first principles of \textit{efficient language use} and
show how this can lead to communicatively efficient systems. We also
demonstrate how assumptions about interlocutors impacts how language
properties are used efficiently. In this way, we bridge questions of
design and use in a single framework.\par

@@

In Simulation 1 we showed that efficiency defined in terms of pragmatic
agents leads to a preference for languages that contain ambiguity. In
Simulation 2 we assume a single fixed language \(\ell\), which contains
ambiguity, and instead vary the types of agents using \(\ell\). We will
show that efficient \emph{use} of ambiguity depends on an agent's
ability to use context for disambiguation. More generally, Simulation 2
is intended to demonstrates how we can assess both questions of
efficient use (current simulation) as well as design (previous
simulation) in the same framework.\par

@@

Figure 3, panel (A) shows the empirical probability a speaker uses an
ambiguous utterance as a function of discourse position. The
\textit{No pragmatic} baseline uses ambiguous utterances frequently and
at a constant rate over the discourse. The \textit{Partial pragmatic}
baseline avoids ambiguous utterances entirely. But, the
\textit{Full pragmatic} model avoids ambiguous material only at the
start of the discourse, employing it increasingly as the discourse
proceeds. Panel (C) tracks our CE objective for each model over the
discourse. Note that the objective decreases for all three models,
primarily driven by the listener updating his belief about the actual
topic (\(P(C=c_{current}|D)\)). However, the objective declines more
quickly under the \textit{Full} and \textit{Partial} pragmatic speakers
as listener agents are better able to infer the correct context.
Additionally, the difference in CE between the \textit{Full}- and
\textit{Partial pragmatic} models at the end of the discourse is driven
by the reduction in speaker costs. Panel (B) tracks speaker effort,
which remains constant in both \textit{No pragmatic} and
\textit{Partial pragmatic} baselines. But, effort declines in the
\textit{Full pragmatic} model as she increasingly relies on ambiguous
material later in the discourse.\par

>>>>

The approaches above typically posit efficiency measures motivated by
information-theoretic principles, but not directly grounded in language
use by interacting agents. In this work, we derive a measure of
efficiency from first principles of \textit{efficient language use} and
show how this can lead to communicatively efficient systems. We also
demonstrate that assumptions about interlocutors impact how language
properties are used efficiently. In this way, we bridge questions of
design and use in a single framework.\par

@@

In Simulation 1 we showed that efficiency defined in terms of pragmatic
agents leads to a preference for languages that contain ambiguity. In
Simulation 2 we assume a single fixed language \(\ell\), which contains
ambiguity, and instead vary the types of agents using \(\ell\). We will
show that efficient \emph{use} of ambiguity depends on an agent's
ability to use context for disambiguation. More generally, Simulation 2
is intended to demonstrate how we can assess both questions of efficient
use (current simulation) as well as design (previous simulation) in the
same framework.\par

@@

Figure 3, panel (A) shows the empirical probability a speaker uses an
ambiguous utterance as a function of discourse position. The
\textit{No pragmatic} baseline uses ambiguous utterances frequently and
at a constant rate over the discourse. The \textit{Partial pragmatic}
baseline avoids ambiguous utterances entirely. But, the
\textit{Full pragmatic} model avoids ambiguous material only at the
start of the discourse, employing it increasingly as the discourse
proceeds. Panel (C) tracks our CE objective for each model over the
discourse. Note that the objective decreases for all three models,
primarily driven by the listener updating his belief about the actual
topic (\(P(C=c_{current}|D)\)). However, the objective declines more
quickly under the \textit{Full} and \textit{Partial pragmatic} speakers
as listener agents are better able to infer the correct context.
Additionally, the difference in CE between the \textit{Full}- and
\textit{Partial pragmatic} models at the end of the discourse is driven
by the reduction in speaker costs. Panel (B) tracks speaker effort,
which remains constant in both \textit{No pragmatic} and
\textit{Partial pragmatic} baselines. But, effort declines in the
\textit{Full pragmatic} model as she increasingly relies on ambiguous
material later in the discourse.\par
